
\section{Reflection}
\label{sec:Reflection}

This project began as an exploration of applying tools from programming language
theory to hardware architecture.  The notion of a hash function for homing
memory to tiles is a well-defined component of a processor and has the advantage
of being relatively abstract, without requiring large amounts of hardware-specific
knowledge.  While we ultimately derived two interesting strategies for this
problem, one of which was indeed based on a tool from programming language
theory, the progress we made was built on a couple of weeks of background
reading as well as a fair amount of trial and error.

We began by reading about caches and homing strategies in manycore designs until
we felt we had a pretty good idea of what the bounds of the problem were.  We
also spent some time reading about hash functions, learning about their
typology, including the universal, cryptographic, and hardware varieties.  On
the programming language front, we decided to explore a synthesis methodology,
and worked to build a few examples of simple synthesis tasks over the theory of
bitvectors.  Throughout our investigating we also learned about how problems
similar to this were addressed in the machine learning space.

Our first few attempts at approaching the problem stalled for a few reasons.
While the requirements of the problem are easy to state in prose, namely that we
want a hash function that distributes memory addresses to tiles according to a
specific distribution in aggregate, that is based on simple bitvector
operations, it was not clear how to state this in our synthesis tool.  During
this back-and-forth process, we ended up tackling the problem from the analytic
approach as well as the synthetic.  It turned out thinking about the problem
from both ends \textit{both} proved worth pursuing, which is how we eventually
were able to provide two distinct solutions to the problem.  The code, sweat,
and tears are all included in the commits of this repo, including programs in
both Racket and Python that may be explored by the interested reader.


